Building Sustainable Software - The CSDMS Approach

### 2014-07-14 paper.tex
Cited overeem et al.

The mission of the Community Surface Dynamics Modeling System (\csdms{})
~\cite{peckham2012component} is to help a diverse modeling community toward
common goals and standards.
%The Community Surface Dynamics Modeling System (\csdms{})
%is an NSF-funded project that began in 2007. Its mission is to help a diverse
%community of surface dynamics model \emph{developers} and model \emph{users}
%work together toward
%common goals and standards.
This effort involves creating:
\begin{itemize}
  \item a repository of source code and metadata for open-source models and
    tools (Section~\ref{sec:organizing})
  \item reusable plug-and-play model components and a framework
        within which these components can be coupled to create new models
        (Section~\ref{sec:reusable})
  \item an efficient and open modeling community through education and
        standards (Section~\ref{sec:education})
\end{itemize}

@@

\subsection{Sustainability and Interoperability Through Standards}

@@

The \csdms{} \emph{Standard Names}\footnote{https://github.com/csdms/bmi}
are a common language for variable names exchanged between models. They play
an important role in the \bmi{} as they provide a mapping of a model's
internal variable names to a common language used by the \bmi{} getter and
setter functions.

@@

Over the last 4 years over 150 graduate students - from geography, hydrology,
geology, oceanography, earth sciences and engineering departments - have
enrolled in intensive \csdms{}-run modeling courses. These courses
provide an excellent use case for us to test usability and access to the
tool. Students reported in post-course surveys that they were unfamiliar with
the use of models on a high performance computing cluster beforehand (rated
their familiarity as 1.5 average on a scale of 1-5), but ended the courses
with familiarity and being more comfortable with running and changing
simulations as well as visualizing results (average rating approaches 4 on
a Likert scale of 1-5).

>>>>

The mission of the Community Surface Dynamics Modeling System (\csdms{})
~\cite{peckham2012component} is to help a diverse modeling community toward
common goals and standards.
%The Community Surface Dynamics Modeling System (\csdms{})
%is an NSF-funded project that began in 2007. Its mission is to help a diverse
%community of surface dynamics model \emph{developers} and model \emph{users}
%work together toward
%common goals and standards.
This effort involves creating:
\begin{itemize}
  \item a repository of source code and metadata for open-source models and
    tools (Section~\ref{sec:organizing})
  \item reusable plug-and-play model components and a framework
        within which these components can be coupled to create new models
        (Section~\ref{sec:reusable})
  \item an efficient and open modeling community through standards (Section
        ~\ref{sec:standards}) and education (Section~\ref{sec:education})
\end{itemize}

@@

\subsection{Sustainability and Interoperability Through Standards}
\label{sec:standards}

@@

The \csdms{} \emph{Standard Names}
\footnote{https://github.com/csdms/standard\_names}
are a common language for variable names exchanged between models. They play
an important role in the \bmi{} as they provide a mapping of a model's
internal variable names to a common language used by the \bmi{} getter and
setter functions.

@@

Over the last 4 years over 150 graduate students - from geography, hydrology,
geology, oceanography, earth sciences and engineering departments - have
enrolled in intensive \csdms{}-run modeling courses. These courses
provide an excellent use case for us to test usability and access to the
tool. Students reported in post-course surveys that they were unfamiliar with
the use of models on a high performance computing cluster beforehand (rated
their familiarity as 1.5 average on a scale of 1-5), but ended the courses
with familiarity and being more comfortable with running and changing
simulations as well as visualizing results (average rating approaches 4 on
a Likert scale of 1-5)~\cite{overeem2013strategies}.
